### 2024-10-22 manuscript.tex
Fix typo

The data sources contained ceilometer observations captured by the Vaisala CL51
 perating at a wavelenght of 910 nm, the Vaisala CT25K operating at 905 nm, and
the Lufft CHM 15k operating at 1064 nm, described in detail below (Sections
\ref{sec:cl51} and \ref{sec:chm15k}). A ceilometer is a low-power near-infrared
vertically pointing lidar with the purpose of measuring the cloud base, but it
also measures the full vertical structure of clouds as long as the laser signal
is not attenuated by thick clouds, which can be used to infer additional
information such as a cloud mask and cloud occurrence by height.

>>>>

The data sources contained ceilometer observations captured by the Vaisala CL51
operating at a wavelenght of 910 nm, the Vaisala CT25K operating at 905 nm, and
the Lufft CHM 15k operating at 1064 nm, described in detail below (Sections
\ref{sec:cl51} and \ref{sec:chm15k}). A ceilometer is a low-power near-infrared
vertically pointing lidar with the purpose of measuring the cloud base, but it
also measures the full vertical structure of clouds as long as the laser signal
is not attenuated by thick clouds, which can be used to infer additional
information such as a cloud mask and cloud occurrence by height.
